---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


From the performance data of 1000 employees, the following are observed:
•	Using tactic A, 24% of employees had improvement in their performance while 76% had degradation.
•	Using tactic B, 23.5% of employees had improvement in their performance while 76.5% had degradation.
•	Tactic A resulted in an average of 67% improvement in employees’ performances, whereas tactic B resulted in an average of 151% degradation in employees’ performances.
From the above observations, it can be seen that the expert may not be correct in their opinion as their opinion is that tactic A resulted in 9% improved performance and 91% degradation, whereas tactic B resulted in 91% degraded performance and 91% degradation. According to me, the data does not suggest that. If at all, tactic A fares better in that on an average, it resulted in 67% better performance of employees. 
Collaborators: Abhijeet, Ananya


